Running `Earth_obs_cleaning` on MCD19A2: Results from CONUS

### 2022-12-22 writing/CONUS_AOD.Rmd
Made a factor-level assignment more predictably correct.

```{r basics, echo=FALSE}
suppressPackageStartupMessages(
  {library(targets)
    library(Just.universal)
    library(data.table)
    library(DT)
    library(patchwork)
    library(ggplot2)
    library(ggridges)
    library(ggpointdensity)
    library(sf)
    library(Just.universal)
    library(knitr)
    library(kableExtra)
    library(RColorBrewer)
    library(SHAPforxgboost)
    # library(flextable)
  })
# set_flextable_defaults(fonts_ignore=TRUE)
source(here::here("code/functions.R"))
source(here::here("code/paper_functions.R"))
the.sat = tools::toTitleCase(Wf$satellite)
```

@@

```{r plot_by_month, echo=FALSE, eval=TRUE, dev='png', dpi=300}
# Color by quantiles
dt[, month := factor(month(time.sat),
                     labels = month.abb)]
p1 <- ggplot(dt, aes(x = y.diff, y = month, fill = factor(stat(quantile)))) +
  stat_density_ridges(
    geom = "density_ridges_gradient", calc_ecdf = TRUE,
    quantiles = 4, quantile_lines = FALSE
  ) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey90") +
  scale_fill_brewer(name = "Quartiles", type = "div") +
  scale_x_continuous("MAIAC AOD minus AERONET AOD", expand = c(0, 0)) +
  coord_cartesian(xlim = c(-0.25, 0.25)) +
  labs(title = paste0("Histogram of difference in colocated AOD (n=",
                      dt[, .N], ")"),
      caption = paste0("Not shown: ", dt[y.diff < -0.25 | y.diff > 0.25, .N], " AOD differences outside [-0.25, 0.25]")) +
  theme_bw()
suppressMessages(print(p1))
```

@@

>>>>

```{r basics, echo=FALSE}
suppressPackageStartupMessages(
   {library(patchwork)
    library(ggridges)
    library(ggpointdensity)
    library(kableExtra)
  })
the.sat = tools::toTitleCase(Wf$satellite)
```

@@

```{r plot_by_month, echo=FALSE, eval=TRUE, dev='png', dpi=300}
# Color by quantiles
dt[, month := structure(class = "factor",
                        month(time.sat),
                        levels = month.abb)]
p1 <- ggplot(dt, aes(x = y.diff, y = month, fill = factor(stat(quantile)))) +
  stat_density_ridges(
    geom = "density_ridges_gradient", calc_ecdf = TRUE,
    quantiles = 4, quantile_lines = FALSE
  ) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey90") +
  scale_fill_brewer(name = "Quartiles", type = "div") +
  scale_x_continuous("MAIAC AOD minus AERONET AOD", expand = c(0, 0)) +
  coord_cartesian(xlim = c(-0.25, 0.25)) +
  labs(title = paste0("Histogram of difference in colocated AOD (n=",
                      dt[, .N], ")"),
      caption = paste0("Not shown: ", dt[y.diff < -0.25 | y.diff > 0.25, .N], " AOD differences outside [-0.25, 0.25]")) +
  theme_bw()
suppressMessages(print(p1))
```

@@

## Comparison with AQS

We examined `r l = tar_read(satellite.vs.aqs); scales::comma(l$nobs)` observations of AQS on `r scales::comma(l$celldays)` cell-days. The correlation of the observations with the original satellite values was `r sprintf("%.03f", l$old)`, compared to `r sprintf("%.03f", l$new)` with our corrected values.
